---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# rutils

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/rutils.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/rutils)
[![R build status](https://github.com/RHReynolds/rutils/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/RHReynolds/rutils/actions)
[![Codecov test coverage](https://codecov.io/gh/RHReynolds/rutils/branch/master/graph/badge.svg)](https://codecov.io/gh/RHReynolds/rutils?branch=master)
<!-- badges: end -->

The goal of `rutils` is to house some of my commonly used functions.

## Installation instructions

There is no plan to ever submit this code to `CRAN` or `Bioconductor`. This code was developed for personal use. If you would like to install the development version from [GitHub](https://github.com/) you can use the following command:

```{r 'install_dev', eval = FALSE}
BiocManager::install("RHReynolds/rutils")
```

## Citation

Below is the citation output from using `citation('rutils')` in R. Please
run this yourself to check for any updates on how to cite __rutils__.

```{r 'citation', eval = requireNamespace('rutils')}
print(citation("rutils"), bibtex = TRUE)
```

Please note that the `rutils` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Code of Conduct

Please note that the `rutils` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## Development tools

* Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/)  through `r BiocStyle::CRANpkg('usethis')`, `r BiocStyle::CRANpkg('remotes')`, and `r BiocStyle::CRANpkg('rcmdcheck')` customized to use [Bioconductor's docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg('BiocCheck')`.
* Code coverage assessment is possible thanks to [codecov](https://codecov.io/gh) and `r BiocStyle::CRANpkg('covr')`.
* The [documentation website](http://RHReynolds.github.io/rutils) is automatically updated thanks to `r BiocStyle::CRANpkg('pkgdown')`.
* The code is styled automatically thanks to `r BiocStyle::CRANpkg('styler')`.
* The documentation is formatted thanks to `r BiocStyle::CRANpkg('devtools')` and `r BiocStyle::CRANpkg('roxygen2')`.

For more details, check the `dev` directory.

This package was developed using `r BiocStyle::Githubpkg('lcolladotor/biocthis')`.


